Appendix B: System size expansion of the master equation for demographic noise

### 2017-10-26 appendixB/appendixB.Rmd
tidy up

However, $\alpha_1'(\phi)$ need not be negative everywhere.  This is easy to see by plotting the macroscopic growth rate $\tfrac{\ud \phi}{\ud t} = \alpha_1(\phi)$ against $\phi$, as in Fig~\ref{levins a1}, where $\alpha_1'$ is simply the slope.  Equilibria $\phi_s$ occur wherever this curve crosses zero.  If it does so with a negative slope, $\alpha_1'(\phi^s) < 0$ then this point is stable.  Hence there will be a region around any stable point where this fluctuation-dissipation relationship given by \eqref{fluctuation dissipation} provides a good description of the fluctuations.  Consequently, for any birth-death process $b>d$ we can write down the equilibrium fluctuations as:

>>>>

However, $\alpha_1'(\phi)$ need not be negative everywhere, but will be negative for any stable point, $\alpha_1'(\phi^s) < 0$.  Hence there will be a region around any stable point where this fluctuation-dissipation relationship given by \eqref{fluctuation dissipation} provides a good description of the fluctuations.  Consequently, for any birth-death process $b>d$ we can write down the equilibrium fluctuations as:
